Gammapy: A Python package for gamma-ray astronomy

### 2023-08-25 src/ms-review.tex
Adapt acknowledgements

        We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
        \texttt{Matplotlib} communities for providing their packages which are
        invaluable to the development of \gammapy. We thank the \github team for
        providing us with an excellent free development platform. We also are grateful
        to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
        documentation hosting and testing respectively. Finally, we would like to thank
        all the \gammapy users that have provided feedback and submitted bug reports.

@@

        A. Donath, R. Terrier, Q. Remy, A. Sinha, C. Nigro, F. Pintore, B. Khélifi, L. Olivera-Nieto, J. E. Ruiz,
        K. Brügge, M. Linhoff and J.L. Contreras contributed to the writing of the manuscript.

        A. Donath, B. Khélifi, C. Boisson, C.Deil, C. van Eldik, D. Berge, E. de Ona Wilhelmi, F. Acero, F. Pintore,
        M. Cardillo, J. Hinton, J.L. Contreras, M. Fuessling, R. Terrier, R. Zanin, R. López-Coto and S. Funk
        are current or former members of the Gammapy coordination committee and contributed to promotion, coordination
        and steering of the \gammapy project.

        A. Aguasca-Cabot, P. Bhattacharjee, K. Brügge, J. Buchner, D. Carreto Fidalgo, A. Chen, M. de Bony de Lavergne,
        A. Donath, J. V. de Miranda Cardoso, C. Deil, L. Giunti, L. Jouvin, B. Khélifi, J. King, J. Lefaucheur,
        M. Lemoine-Goumard, J.P. Lenain, M. Linhoff, L. Mohrmann, D. Morcuende, C. Nigro, L. Olivera-Nieto,
        S. Panny, M. Regeard, Q. Remy, J. E. Ruiz, L. Saha, H. Siejkowski, A. Siemiginowska, A. Sinha,
        B. M. Sipőcz, R. Terrier, T. Unbehaun, T. Vuillaume contributed to the code development of \gammapy.

>>>>

        We would like to thank the \texttt{Numpy}, \texttt{Scipy}, \texttt{IPython} and
        \texttt{Matplotlib} communities for providing their packages which are
        invaluable to the development of \gammapy. We thank the \github team for
        providing us with an excellent free development platform. We also are grateful
        to Read the Docs (\ReadthedocsUrl), and Travis (\TravisUrl) for providing free
        documentation hosting and testing respectively. We would like to thank
        all the \gammapy users that have provided feedback and submitted bug reports.

@@

        For contributing to the writing of the manuscript, we thank A. Donath, R. Terrier, Q. Remy, A. Sinha,
        C. Nigro, F. Pintore, B. Khélifi, L. Olivera-Nieto, J. E. Ruiz, K. Brügge, M. Linhoff and J.L. Contreras.

        We also thank the current and former members of the Gammapy coordination committee A. Donath, B. Khélifi,
        C. Boisson, C.Deil, C. van Eldik, D. Berge, E. de Ona Wilhelmi, F. Acero, F. Pintore,
        M. Cardillo, J. Hinton, J.L. Contreras, M. Fuessling, R. Terrier, R. Zanin, R. López-Coto and S. Funk,
        who contributed to promotion, coordination and steering of the \gammapy project.

        Finally we would like to thank A. Aguasca-Cabot, P. Bhattacharjee, K. Brügge, J. Buchner, D. Carreto
        Fidalgo, A. Chen, M. de Bony de Lavergne, A. Donath, J. V. de Miranda Cardoso, C. Deil, L. Giunti,
        L. Jouvin, B. Khélifi, J. King, J. Lefaucheur, M. Lemoine-Goumard, J.P. Lenain, M. Linhoff,
        L. Mohrmann, D. Morcuende, C. Nigro, L. Olivera-Nieto, S. Panny, F. Pintore, M. Regeard,
        Q. Remy, J. E. Ruiz, L. Saha, H. Siejkowski, A. Siemiginowska, A. Sinha, B. M. Sipőcz, R. Terrier,
        T. Unbehaun, T. Vuillaume and unnamed contributors for contributing to the development of \gammapy.
